---
title: "MissingData"
author: "Lydia Suter"
date: "2/10/2022"
output: word_document
---
```{r}
library(tidyverse)
library(tidymodels)
library(mice) #package for imputation
library(VIM) #visualizing missingness
library(naniar)
library(skimr)
```

```{r}
grades <- read_csv("class-grades.csv")
```
```{r}
str(grades)
summary(grades)

```
Task 1: Fo which variables is there missing data? tutorial-1,midterm-3,takehome-3, finals_4

Task 2: Use the VIM package to visualize missingness. Are there any students that are missing multiple
pieces of data? yes
```{r}
vim_plot = aggr(grades, numbers = TRUE, prop = c(TRUE, FALSE),cex.axis=.7)
```
```{r}
vis_miss(grades) #from the naniar package
```
```{r}
gg_miss_case(grades) #x axis is number of missing values in each row (case)
```
Task 3: Use row-wise deletion of missing values to create a new data frame. How many rows remain in
this data frame?89
```{r}
grades_rowdel = grades%>% drop_na() 
#alternatively can specify which variable(s) on which to do the drop_na
#drop_na(Age)
skim(grades_rowdel)
```

Task 4: Use column-wise deletion of missing values to create a new data frame (from the original data
frame not from the data frame created in Task 3). How many columns remain in this data frame?2
```{r}
grades_coldel = grades %>% select(-Tutorial,-Midterm,-TakeHome,-Final) 
vim_plot = aggr(grades_coldel, numbers = TRUE, prop = c(TRUE, FALSE),cex.axis=.7)
skim(grades_coldel)
```
Task 5: Which approach (Task 3 or Task 4) seems preferable for this dataset? Briefly discuss your answer.row-wise deletion

Task 6 Use the “mice” package to impute the missing data in this dataset. Set “m = 5” and “method
=”pmm"" in the imputation. You MUST use a random number seed of 123 for this imputation. What is the
mean value for the “Final” variable after imputation?
```{r}
set.seed(123) #sets seed for random number generator
imp_grades = mice(grades, m=5, method='pmm', printFlag=FALSE)
#m is the number of imputations, 5 is a reasonable value as a default
#pmm is "predictive mean matching" = imputation method for numeric data
#printFlag reduces amount of output
summary(imp_grades)
```
```{r}
grade_complete = complete(imp_grades) 
summary(grade_complete)
```

